MG7: Configurable and scalable 16S metagenomics data analysis -- new methods optimized for massive cloud computing

### 2015-10-11 docs/paper/out/paper.tex

>>>>

\section{Figure 1: MG7 analysis
workflow.}\label{figure-1-mg7-analysis-workflow.}

The paired reads in fastq format are merged resulting in only one
sequence per read pair. The next step is a parallelized BLASTN of every
merged sequence against the 16S reference database 16S-DB7. Then, the
mapping of the detected similar sequences in the database to the
taxonomy node to which they belong is carried out. This is done using
Bio4j that includes a module with all the NCBI taxonomy in a graph
connected with the Gene Ontology, Uniprot, and RefSeq graphs. Then the
taxonomic assignment is done for each sequence following two different
approaches: LCA and BBH, and finally the abundances corresponding to
direct and cumulative assignments for each node in percentage and
absolute counts are provided for each assignment mode.

\section{Figure 2: Lowest Common Ancestor algorithm for taxonomic
assignment.}\label{figure-2-lowest-common-ancestor-algorithm-for-taxonomic-assignment.}

The Left panel displays an example of the application of LCA algorithm
in a \emph{sensu stricto} mode. A, B, C and D represent taxonomy tree
nodes with assigned reads. Right panel displays the \emph{in line} mode
of assignment which is an exception for the \emph{sensu stricto} mode of
application of LCA algorithm. The \emph{in line} mode is used when all
the nodes are located in a line without bifurcations. In that case the
taxon assigned is the most specific (the most distant from the root).
